SPP-Perc: Peceptron Learning Based Enhanced Signature Path Prefetcher

### 2018-12-07 related.tex
updated grammar, last paragraph still needs work

Unlike spatial prefetchers, lookahead prefetchers take program order into
account when they make predictions. Shevgoor \textit{et al.} proposed the Variable 
Length Delta Prefetcher (VLDP)~\cite{VLDP} that correlates histories of
deltas between cache line accesses within memory pages with the next delta
within that page. SPP~\cite{SPP} and KPC's prefetching component~\cite{KPC} are
more recent examples of lookahead prefetchers. They try to predict not only what
data will be used in the future, but also the precise order in which the data
will be used, within a given page. Predictions made by lookahead prefetchers can
be fed back into their prediction mechanisms to predict even further down 
a speculative path of memory acesses. These prefetchers can also generalize their
learned patterns from one page, and use those patterns to make predictions in 
other pages.

>>>>

Unlike spatial prefetchers, lookahead prefetchers take program order into
account when they make predictions. Shevgoor \textit{et al.} propose the Variable 
Length Delta Prefetcher (VLDP)~\cite{VLDP}, which correlates histories of
deltas between cache line accesses within memory pages with the next delta
within that page. SPP~\cite{SPP} and KPC's prefetching component~\cite{KPC} are
more recent examples of lookahead prefetchers. They try to predict not only what
data will be used in the future, but also the precise order in which the data
will be used, within a given page. Predictions made by lookahead prefetchers can
be fed back into their prediction mechanisms to predict even further down 
a speculative path of memory acesses. These prefetchers can also generalize their
learned patterns from one page, and use those patterns to make predictions in 
other pages.
